---
# This is page header
title: "This is my work in R" 
author: "MyFirstName MyLastName, OrganizationName, username@the.rest"
#date: '`r format(Sys.time(), "%B %d, %Y")`' #automatic
date: "August 23, 2022" #manually
abstract: "This is an example of an abstract in a paper. This is an example of an abstract in a paper.This is an example of an abstract in a paper. This is an example of an abstract in a paper.This is an example of an abstract in a paper.This is an example of an abstract in a paper.This is an example of an abstract in a paper."

fontsize: 12pt

#setup of webpage output
output:
  bookdown::html_document2
  
# for bibliography
bibliography: FGVexample.bib
biblio-style: apalike
#csl: apa.csl
---

<br> <!--this is a line break-->

<!-- a chunk hidden (echo=FALSE) with some setup-->

<!-- chunk has its own name -->

```{r someSetup, echo=FALSE}
# clean memory
rm(list = ls())
# for cropping figures
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)

# github data folder:
link1="https://github.com/profemagallanes-unmsm/"
link2="FGV_Python_prepublish/raw/main/DataFiles/"
where=paste0(link1,link2)
```

<!-- use "-" to unnumber -->

# Introduction {.unnumbered}

This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.

This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.This is just my intro to my nice paper. This is just my intro to my nice paper.

<!--label for crossref-->

# Exploring Tables {#explo-tables}

<!--footnote coming-->

Another section. I will use a footnot now [^1]. I will soon use cross-ref.I will soon use cross-ref.I will soon use cross-ref.I will soon use cross-ref. I will soon use cross-ref. I will soon use cross-ref.I will soon use cross-ref.I will soon use cross-ref.I will soon use cross-ref.I will soon use cross-ref. I will soon use cross-ref. I will soon use cross-ref.

[^1]: This is a footnote.

<!--cross-ref coming-->

I will soon use cross-ref.I will soon use cross-ref: as we see in Section \@ref(catexplor).

```{r collecting_DataTable, echo=FALSE}
fileLink=url(paste0(where,"mergedData.RDS"))
mergedData=readRDS(fileLink)
```

## Exploring Categorical Data {#catexplor}

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

You can see the statistics of categorical variables in Table \@ref(tab:catexploreTable).

<!--the chunk name  IS USED in cross-ref for TABLES, SEE above-->

<!-- Table is created and displayed. -->

```{r catexploreTable,results='asis', warning=FALSE, echo=FALSE}
## display frequency table of Freedom Index
library(summarytools)
library(tidyr)
library(knitr)
library(kableExtra)

namesHeaders=c("Democracy Index","count","pct","pct_cumm")
freq(mergedData[, 9], 
     plain.ascii = FALSE,
     report.nas=FALSE) %>%
    ## changes, we need data frame
    tb() %>%
     kable(format = "html", 
           digits = 2,
           caption = "This is a table", #no label here
           col.names = namesHeaders)%>%
     kable_styling(full_width = F)
```

You can see this variable plotted in Figure \@ref(fig:catBarplot).

<!--Figure caption in chunk header is a MUST-->

<!-- Object will be created and plotted -->

<!--the chunk name is used in cross-ref for FIGURE-->

```{r prepare_catBarplot,echo=FALSE}
## prepare frequency table as data frame
theTable_Free=table(mergedData$PressFreedomIndex_or)
theTable_Free_asDF=as.data.frame(theTable_Free)
names(theTable_Free_asDF)=c("var","count") #renaming
```

```{r catBarplot, fig.cap="Freedom of Press in the world",echo=FALSE}
library(ggplot2)
base=ggplot(data=theTable_Free_asDF,aes(x=var,y=count))
bar1=base + geom_bar(stat = 'identity')
bar1=bar1+labs(x="Press Freedom")
##plotting
bar1
```

## Exploring Numerical Data {#numexplo}

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

```{r summaryNumeric, results='asis', message=FALSE,echo=FALSE}
## table of summary statistics
library(vtable)
st(mergedData[,c("DemocracyIndex","mili_pctGDP")],
   title ="Stat summary for nummeric vars",
   digits = 2)
```

<!-- Use of R object inline -->

In the Table \@ref(tab:summaryNumeric), you realize that the mean of military expenditure is **`r mean(mergedData$mili_pctGDP)`**.

It would be good to see a boxplot, check Figure \@ref(fig:numBoxplot) below.

```{r numBoxplot,fig.cap='Money spent per country on Military stuff' ,echo=FALSE}
base=ggplot(data=mergedData)
box = base + geom_boxplot(aes(y=mili_pctGDP)) 
box = box + labs(x="", y = "% of country GDP")
box=box + theme(axis.text.x = element_blank(),
                axis.ticks.x = element_blank())
## plotting
box
```

<!--- A citation: author(year) --->

Boxplots were introduced by [@tukey_exploratory_1977].

# My Regression

Several times we need regression.

```{r regresPrep, echo=FALSE}
## prepare regressions
h1=formula(mili_pctGDP~DemocracyIndex)
regre1=lm(h1,data=mergedData)

h2=formula(mili_pctGDP~DemocracyIndex + IndexofEconomicFreedom)
regre2=lm(h2,data=mergedData)
```

This is a nice summary for two regressions, as shown in Table \@ref(tab:regs1):

```{r regs1,results='asis', echo=FALSE}
## show result of both
library(modelsummary)

models=list(regre1,regre2)
modelsummary(models, 
             title = "Models for Military Expenditure",
             stars = TRUE,
             output = "kableExtra")
```

You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:

```{r regs2, echo=FALSE,results='asis'}
## show result of both BETTER
cm <- c('DemocracyIndex'='Democracy',
        'IndexofEconomicFreedom'= 'Economic Freedom',
        '(Intercept)' = 'Constant')
modelsummary(models, 
             title = "Models for Military Expenditure",
             stars = TRUE,
             output = "kableExtra",coef_map = cm)
```

I hope you like what you see in the Table \@ref(tab:regs1) and in Table \@ref(tab:regs2). You can learn more on regression in other book [@petrie_introduction_2016,150-160].

# Other plots {#otherPlots}

## A word cloud {#wordPlot}

Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud. Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.

```{r collecting_DataForCloud, echo=FALSE}
location=paste0(where,'rebelData.csv')
wordData=read.csv(location)
```

```{r prepareDataForCloud, echo=FALSE}
library(tidyr)
wordDataNames=separate_rows(wordData,StateName) # key process
stateCounts=as.data.frame(table(wordDataNames$StateName))
names(stateCounts)=c("state","aCount")
```

```{r theCloudPlot, echo=FALSE, fig.cap="Nations by presence of rebel movements.",crop=TRUE}
library(ggwordcloud)

set.seed(123)
base = ggplot(stateCounts, aes(label = state,
                               size= aCount,
                               color = aCount))
cloudRebel= base + geom_text_wordcloud() + theme_minimal()
cloudRebel= cloudRebel+scale_color_gradient(low = "orange",
                                            high = "red") 
cloudRebel
```

Above you see our Figure \@ref(fig:theCloudPlot). Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it.

It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it.

You can read something interesting somewhere else [@lipman_art_2022].

## A map {#map}

Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.

Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.

Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map in Figure \@ref(fig:theMapPlot).

```{r collecting_DataMap, echo=FALSE,message=FALSE}
fileMapPoints=paste0(where,"calls911_geo.geojson")
fileMapPolygons=paste0(where,"MapSeattle.geojson")

library(ggplot2)
library(sf)
events=read_sf(fileMapPoints)
city=read_sf(fileMapPolygons)
```

```{r theMapPlot, echo=FALSE, fig.cap="Calls to 911 by time of day",message=FALSE}

base=ggplot(city) + geom_sf() + theme_light()
eventsByTime=base + geom_sf(data = events,
                         size=0.5,
                         aes(color=nightTime)) 
eventsByTime
```

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it.

<!--- more than one author in a citation --->

Review other authors [@camara_spatial_nodate, 120-150; also, see @brunsdon_introduction_2015] to know more.

# Bibliography {.unnumbered}

```{=html}
<!--
<div id="refs"></div>
-->
```
